---
title: "DataOrganizationSynapse"
output: rmarkdown::github_document
---

## Few words about getting started Synapse

This is just for my own short RAM that I am unable to upgrade and if it helps anybody else too.

* I consider Synapse as data-Github- I would prefer to keep all versions scripts in Git and all different versions of data in Synapse

* I prefer to use markdown files instead of scripts files as well unless i am integrating a full workflow.

For getting started follow some introductions here:

* https://r-docs.synapse.org/articles/synapser.html
* https://r-docs.synapse.org/articles/synapser.html
* To access synExtra at git: https://github.com/ArtemSokolov/synExtra
* Examples of setting up synapse config files parameters @ https://github.com/Sage-Bionetworks/synapsePythonClient/blob/master/synapseclient/.synapseConfig

* We have three options to set up login. If you dont need to deal with other clients frequently e.g AWS-S3 etc synLogin is enough otherwise you can setup configuration file as mentioned above.

* By default data downloaded from Synapse is cached at user’s home directory and is called .synapseConfig unless specified; We can fix it in .synapseConfig file to a new  cache location too.

* Note:does not work with reticulate package in one session 

```{r message=FALSE}
#install.packages("synapser", repos = c("http://ran.synapse.org", "http://cran.fhcrc.org"))
#if( !require(devtools) ) install.packages( "devtools" )
#devtools::install_github( "ArtemSokolov/synExtra" )
library(synapser)
library(synExtra)
```

## login to Synapse 
How to configure login details Long Story read @https://r-docs.synapse.org/articles/manageSynapseCredentials.html

short story here 

* if you have a synapse account registered 
* pass your username and password for synapse in synLogin function e.g. "synLogin("username", "password",rememberMe=True))"
* you just need to do it once and from next time you will not have to enter your username or password like below
```{r}
synLogin()
```


### Updating a data directory with complex structure in Synapse 

library(synExtra) has all the cool things to do here for us.

To add a new directory with all complex directory structure:

* pass the synapse project id and local path  

* still playing with versions : pulled the issue 

* read more on versions of files @ https://docs.synapse.org/articles/files_and_versioning.html

```{r}
synExtra::synStoreMany( "/Users/siddia/Desktop/SynapseTestProject", parent="syn24215009")
  
## The function understands local paths
#synExtra::synStoreMany( ".", "syn12180284" )

## As well as relative paths
#synExtra::synStoreMany( "../myOtherFolder", "syn12180284" )
```

```{r}
#project <- Project( "TestProjectAmnah")
#project <- synStore(project)
```


```{r}
#project <- Project( "TestProjectAmnah")
#project <- synStore(project)
```

##  

You can also embed plots, for example:

```{r }
# #Adding files to the project:
#   filestoupload<-list.files("/Users/siddia/Google Drive/Codes2020_SiddiqaAmnah/Synapse/CiberSort/")
#   path=("/Users/momo/Google Drive/Literature/AntibodyResponsePredictionBaseline/HIPCCHI/")
#   
#   
#   
#   #dataFolder can be a child folder or project itself 
#   for(i in 1:length(filestoupload)) {
#   file <- File(path = paste0(path,filestoupload[i]), parent = "syn23532082")
#   file <- synStore(file)
#   }
```


```{r }
# Load required libraries
# library(synapser)
# library(synapserutils)

# login to Synapse
#synLogin(email='me@example.com', password='secret', rememberMe=TRUE)
# synLogin()
# download all the files in folder syn123 to a local folder called "myFolder"
#all_files = syncFromSynapse(entity='syn24215009', path='/Users/siddia/Desktop/SynapsePlaying')
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
